Analysis

### 2023-03-03 analysis/analysis.Rmd
incorporate final edits

# save(p_response, herit_plot, p_beta, p_log10, file = here(der_dir, 'plots.RData'))
save(response_model, compare_response_mods, per_slope, rh_model, kt, wt, rare_median, s5, min_seqs, tidy_permanova, dbrda_aov, dbrda_percent_explained, da_fams, file = here(der_dir, 'models.RData'))

>>>>

#save(p_response, herit_plot, p_beta, p_log10, file = here(der_dir, 'plots.RData'))
save(response_model, compare_response_mods, per_slope, rh_model, kt, wt, rare_median, s5, min_seqs, tidy_permanova, dbrda_aov, dbrda_percent_explained, da_fams, file = here(der_dir, 'models.RData'))
